Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-01-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates on abstract and conclusions

%%%%%%%%%%%%%
\section{Conclusions}\label{Section:Conclusion}
\red{KOSTAS: Conclusions of numerical modelling papers are are often very short and divided into 3 parts: (1) Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by \underline{your work} in the present manuscript; (2) Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory); and (3) (optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}

%A number of different cases have been illustrated in Section \ref{section:results}. Starting from testing experimental cases and geometrical domains (Hele-shaw domain) to verify that the numerical model is working and set up some initial benchmarks, to more complicated cases where various scenarios were implied. Observations made on various mobility ratios, geometrical domains and permeability zones as well as on the role of interfacial forces and fingering mechanisms on the developement of the flows.

\medskip
For immiscible displacements upon which only viscous and capillary forces are acting, the expected displacement patterns are either fully developed cross flow displacement or unstable front displacement. In the latter case the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but mainly is a fuction of viscocity ratio (\ie VR). If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates.

@@

\medskip
In summary, the method that has been described in this paper as well as the simulations performed have a number of distinct advantages: 
\begin{enumerate}
\item[1.] The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and to the fact that the geological characteristic and parameters can be easily introduced.
\item[2.] Computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate and manage using fewer grid cells. The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.
\item[3.] Production simulations run directly on the geological model without the need to upscale.\\
\end{enumerate}

@@

>>>>

%%%%%%%%%%%%%
\section{Conclusions}\label{Section:Conclusion}
\red{(1)Short (1 paragraph) summary of the paper with focus on the main theoretical aspects that were proved by our work in the present manuscript;}
The purpose of this paper is to describe the fluid instabilities, in particular the viscous fingering, and demonstrate a new computational approach used in order to capture the finger development. Starting from validating the development of fingers in a computational domain against experimental setup a series of other computational cases is showed focusing on the details of the flows and the introduction of parameteres by avoiding any upscaling requirements.

\red{(2)Summary (1-3 paragraphs) of the main results with the appropriate analysis (\ie how you work has proved the theory);}
\medskip
By definition the instability rises due to viscous fingering depending on capillary number ($N_{c}$) but is also a direct fuction of viscocity ratio (\ie VR). If the mobility ratio is significantly less than $5$, it is expected to find capillary fingering at relatively low flow rate and viscous fingering at relatively high flow rate. On the other hand, when the viscosity ratio is greater than $5$, the two basic forms of immiscible displacement are capillary fingering at relatively low flow rate and stable displacement at relatively high flow rate. Therefore for an \ie water/oil system, the first condition applies as the viscosity of injected water is less than the viscosity of displaced oil. Hence, the displacement front could be either capillary fingering at relatively low injection rates or viscous fingering at higher injection rates. The method that has been described in this paper as well as the simulations performed have a number of distinct advantages; (1.) The geological model can be designed from the beginning without any previous reference or geometrical limitations due to both the flexibility of method and because the geological characteristic and parameters can be easily introduced without the need of upscaling while, (2.) computational cost can be reduced, because the complex geometries and surfaces are less expensive to generate (unstructured grid in space and time) and manage using fewer grid cells. The basis of the this argument is the flexibility and variance of the adaptive and unstructured grid in time and space.

@@

@@

\red{(3)(optional) 1 paragraph of potential future work. Make sure that (1) and (2) are covered in the present Section.}
